---
title: "Data Products - Argentina 2017 imports of phys/chem analysis apparatus"
author: "Stephen Gillanders"
date: "9/28/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r libraries,echo=FALSE,message=FALSE,results=FALSE}
library(leaflet)
library(tidyr)
library(Hmisc)
```
## Data Source

The data on imports comes from the Argentine Government's National Institute for Statistics and Census (INDEC).

The data can be found from this [link](https://comex.indec.gov.ar/search/imports/2017/Y/90278099/C). You should see a text "Se encontraron 40 resultados, haga click aqui para descargarlos.": click on it to retrieve the data. The product code "90278099" is for "Instrumentos y aparatos p/analisis fisicos o quimicos. ncop", i.e. "Instruments and apparatus for physical or chemical analysis".

I changed the column headings in the file to:
"Year";"NCM";"Product";"Country";"Net.weight";"USD.CIF".
where:

- Year =  2017
- NCM = product code according to Mercosur Common Nomenclature (fixed: 90278099)
- Product = product description (fixed: "Instrumentos y aparatos p/analisis fisicos o quimicos, ncop.")
- Country = Original Spanish name translated to English by me
- Net.weight = Kg, total
- USD.CIF = total value in US Dollars, CIF

Country data (for latitude and longitude) was taken from [google dataset publishing language](https://developers.google.com/public-data/docs/canonical/countries_csv) countries.csv by importing HTML_tables into OpenOffice and saving as a .csv file.


```{r read_data}
df <- read.csv("Importaciones_2017.csv",sep=";",header=TRUE)
dfc <- read.csv("countries_google.csv",sep=";",header=TRUE)
head(df[,-3],4)
head(dfc,4)
```
```{r process_data}
tdf <- merge(df,dfc,by.x="Country",by.y="name")
tdf$popup <- paste("<b>",tdf$country,"/",
                   tdf$Country,
                   "</b><br>Total imports (USD): ",format(tdf$USD.CIF,big.mark=","))
tdf$quant <- cut2(tdf$USD.CIF,g=10)
tdf$radius <- as.numeric(tdf$quant)*50000
```

## Map of imports to Argentina by country of origin

```{r imports_plot, echo=FALSE}
heatc <- heat.colors(10)
pal <- colorFactor(heatc,tdf$quant)
my_plot <- tdf %>% leaflet() %>% addTiles() %>% 
    addCircles(lat=~latitude,lng=~longitude,
               popup=~popup,
               radius=~radius,
               color=~pal(quant)) %>%
    addLegend("bottomright",colors=heatc,
              labels=levels(tdf$quant),
              title="Imports (USD)",
              opacity=1)
my_plot
```

